---
title: "Compare two weighted synthetic files with PUF"
date: "`r format(Sys.time(), '%B %d, %Y')`"  # "`r Sys.Date()`"
output:
  html_notebook:
    df_print: paged
    fig_height: 7
    fig_width: 9
    toc: yes
  html_document:
    fig_height: 7
    fig_width: 9
    toc: yes
    toc_depth: 5
---


```{r notes, include=FALSE}
# CAUTION: yaml requires proper indentation with spaces or this will become (I think) a regular R markdown file
# It can be hard to get tables to work properly. It seems like it is best to have chunk output inline.

# https://pslmodels.github.io/Tax-Calculator/

```


```{r setup, include=FALSE}
# force the working directory for the notebook file to be the wd of the project - see:
# https://support.rstudio.com/hc/en-us/community/posts/220826588-Working-directory-in-R-Notebooks
#  also see the following, which does not look as good
# https://stackoverflow.com/questions/44816945/why-setting-working-directory-in-r-notebook-doesnt-change-working-directory-in
# knitr::opts_knit$set(root.dir = normalizePath("path")) # wherre path is desired wd

# knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())

knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE)
# knitr::opts_chunk$set(fig.width = ..., fig.height = ...)

```


```{r clear_warnings, eval=FALSE}
# run this line to clear any old warning messages
# assign("last.warning", NULL, envir = baseenv())
```


```{r libs, include=FALSE}
# source("./r/includes/libraries.r")
source(file.path(PROJHOME, "r/includes", "libraries.r"))
# library("readxl")
library("knitr")

# search() %>% sort # how did precis get loaded?

source(file.path(PROJHOME, "r/includes", "globals_system_specific_boyd.r"))
source(file.path(PROJHOME, "r/includes", "globals_other.r"))
source(file.path(PROJHOME, "r/includes", "functions_general.r"))

```


```{r define_comparison_files, include=FALSE}
synname <- "synthpop10" # synthpop stacked file
synpufname <- "synpuf20"  # Max's synpuf file

```


```{r define_income_ranges, include=FALSE}
iranges <- c(-Inf, 0, 25e3, 50e3, 75e3, 100e3, 200e3, 500e3, 1e6, 10e6, Inf)
irange_labs <- c("<= 0",
                 "> 0  to     25k",
                 "> 25k to     50k",
                 "> 50k to     75k",
                 "> 75k to    100k",
                 "> 100k to    200k",
                 "> 200k to    500k",
                 "> 500k to  1,000k",
                 "> 1,000k to 10,000k",
                 "> 10,000k")

#  mutate(wrange=cut(e00200, iranges, labels=irange_labs))

```


```{r get_vnames, include=FALSE}
puf.vnames <- get_puf_vnames()

psum <- get_pufbase_sums()
# psum
# psum %>% arrange(vname)
```


```{r get_comparison_files, eval=FALSE}
# get puf, cart, and rf files
cartname <- "synthpop10_wfs.rds"
cartstackname <- "synthpop10_wfs_stack.rds"

# rfname <- "synpuf20_wfs.rds"
rfname <- "synpuf20_lowmatch_wfs.rds"

cstack <- readRDS(paste0(globals$tc.dir, cartstackname))
glimpse(cstack)
names(cstack) %>% sort
summary(cstack %>% select(starts_with("wt"))) # wt is what we want
count(cstack, ftype)

rf <- readRDS(paste0(globals$tc.dir, rfname))
glimpse(rf)
names(rf) %>% sort
summary(rf %>% select(starts_with("wt"))) # wt is what we want
count(rf, ftype)

stack <- bind_rows(cstack %>% 
                     mutate(ftype=ifelse(ftype=="syn", "cart", ftype)),
                   rf %>% mutate(ftype="rf")) %>%
  mutate(ftype=factor(ftype, levels=c("puf", "cart", "rf")), # desired sort order
         wfsrecid=RECID,
         RECID=row_number(), # allows us to link tc results to input
         msname=fct_collapse(as.factor(MARS),
                         single="1",
                         married="2",
                         other=c("3", "4")))
glimpse(stack)
# saveRDS(stack, paste0(globals$tc.fir, "test_stack.rds"))

count(stack, ftype, msname) %>%
  spread(ftype, n)

```


```{r ONETIME_run_reforms, eval=FALSE}
# reform <- "rate_cut"
# reform <- "toprate"
# reform <- "EITC"
# reform <- "Trump2013"
# reform <- "rt5_2013"
# rt4_rate28_2013
# reform <- "brk4_2013"
# reform <- "brk4_1k_2013"
# reform <- "brk4_10k_2013"

# reform <- "amtex_2013"
# reform <- "amtex10k_2013"
# reform <- "amtex_taxbrain_2013"
# tuition0320_2013
# rt4_rate28_2013

# flabel <- "synth10_syn20"
# reforms <- c("rate_cut", "toprate", "Trump2013", "EITC")
reforms <- c("rate_cut", "Trump2013", "toprate", "rt5_2013", "rt4_rate28_2013", "brk4_2013", "brk4_10k_2013", "reform4")

runtc <- function(reform, source.fn){
  taxplan.fn <- paste0(reform, ".json")
  system.time(ref <- run_taxplan_getresults(source.fn, taxplan.fn))
  # ~20 mins puf + 2 syn w/5x each
  # saveRDS(ref, paste0(globals$tc.dir, runname, "_", reform, ".rds"))
}

# ONETIME run the baseline tax on the stacked file ----

reform <- reforms[6]
reform <- "rate_cut"

# source.fn <- "synth10syn20_small.csv" # DO NOT WRITE THIS TO DISK
# source.fn <- "synth10syn20.csv"
source.fn <- "lowmatch.csv"


# ONETIME for each new combination of files making up stack ----
# IF NEEDED take the already prepared stack file and write it to a directory that all parallel processes can read ----
write_csv(stack, paste0(globals$tc.dir, source.fn))
saveRDS(stack, paste0(globals$tc.dir, str_remove(source.fn, ".csv"), "_stack.rds"))
# run the baseline tax on the stacked file
run_taxplan_getresults(source.fn) # write output to csv and rds files
# END ONETIME ----

#.. run it in parallel ----
library("doParallel")
cl <- makeCluster(6)
registerDoParallel(cl)

packages <- c("magrittr", "tidyverse", "dplyr")
# CAUTION:  DO NOT PASS large items as function arguments
# instead export them
xport <- c("globals", "source.fn", "run_taxplan_getresults", "tc.wincmd") 
popts <- list(.packages=packages, .export=xport)
popts

# now run in parallel
a <- proc.time()
warn <- options()$warn
options(warn=-1)
l_ply(reform, .progress="text", .parallel=FALSE, .paropts=popts, .fun=runtc, source.fn=source.fn)
options(warn=warn)
b <- proc.time()
b - a

stopCluster(cl)

# looping through child documents
# https://gist.github.com/rmoff/a043676a2f084b81a434

```


```{r top_vars, include=FALSE}
# define top income and deduction variables
psum
# e00200 e01500 e02400 e02000
# e19200 e18400 e18500 e19700 [not in stack] e19800
incvars <- c("e00200", "e01500", "e02400", "e02000", "e26270")
dedvars <- c("e19200", "e18400", "e18500", "e19800", "e17500")
setdiff(incvars, names(stack))
setdiff(dedvars, names(stack))

# get the baseline file against which we will compare the reforms ----
# c00100 AGI
# c17000 Sch A: Medical expenses deducted
# c18300 Sch A: State and local taxes deducted
# c21060 Itemized deductions before phase-out (zero for non-itemizers)
# standard Standard deduction (zero for itemizers)
# c04800 Regular taxable income
# taxbc regular tax before credits
# c09600 Alternative Minimum Tax (AMT) liability
# c05800 taxbc plus AMT liability

tcvars <- c("c00100", "standard", "c17000", "c18300", "c21060", "c04800", "taxbc", "c09600", "c05800")
#stack <- readRDS(paste0(globals$tc.dir, "synth10syn20_stack.rds"))
#stacktax <- readRDS(paste0(globals$tc.dir, "synth10syn20__output.rds"))
# lowmatch_rate_cut_output.rds
stack <- readRDS(paste0(globals$tc.dir, "synpuf20_lowmatch_wfs_stack.rds"))
stacktax <- readRDS(paste0(globals$tc.dir, "lowmatch__output.rds"))
glimpse(stack)
glimpse(stacktax)
baseline <- stack %>%
  select(-one_of(tcvars)) %>%
  left_join(stacktax %>% select(RECID, tcvars), by="RECID")

```


```{r tab_functions, include=FALSE}
# "rate_cut"  "Trump2013" "toprate"   "rt5_2013"  "brk4_2013" "rt4_rate28_2013"
reforms <- c("rate_cut", "Trump2013", "toprate", "rt5_2013", "brk4_2013", "reform4", "amtex_2013", "tuition0320_2013", "rt4_rate28_2013")

get_mrgdf <- function(reform, refbase="synth10syn20"){
  refname <- paste0(refbase, "_", reform, "_output.rds")
  refdf <- readRDS(paste0(globals$tc.dir, refname))
  
  mrgdf <- left_join(baseline,
                     refdf %>% dplyr::select(RECID, 
                                             c00100.reform=c00100, # calculated AGI
                                             taxbc.reform=taxbc, # regular tax liability before credits
                                             c09600.reform=c09600, # AMT liability
                                             c05800.reform=c05800), # regular tax liability + AMT
                     by="RECID") %>%
    mutate(reform_name=reform)
  return(mrgdf)
}

dtot <- function(df){
  dsums <- df %>% 
    summarise_at(vars(-reform_name, -ftype, -agirange), ~sum(.)) %>%
    mutate(reform_name=df$reform_name[1],
           ftype=df$ftype[1], 
           agirange="Total")
  dfout <- bind_rows(df, dsums)
  return(dfout)
}


get_diffs <- function(mrgdf){
  diffs <- mrgdf %>%
    mutate(agirange=cut(c00100, iranges, labels=irange_labs)) %>%
    group_by(reform_name, ftype, agirange) %>%
    summarise_at(vars(c05800, c05800.reform), funs(sum(. * wt) / 1e9)) %>%
    do(dtot(.)) %>%
    mutate(agirange=factor(agirange, levels=unique(agirange), ordered=TRUE),
         diff=c05800.reform - c05800,
         pdiff=diff / c05800 * 100) %>%
    ungroup
  return(diffs)
}


tab_c05800 <- function(diffs, pdigits=c(0, 0, rep(1, 7))) {
  tab <- diffs %>%
    select(reform_name, ftype, agirange, value=c05800) %>%
    spread(ftype, value) %>%
    mutate(cart.diff=cart - puf,
           rf.diff=rf - puf,
           cart.pdiff=cart.diff / puf * 100,
           rf.pdiff=rf.diff / puf * 100) %>%
    kable(caption="Tax before credits, baseline, $ billions",
          digits=pdigits,
          format.args=list(big.mark=",")) %>%
    kable_styling(full_width = FALSE)
  return(tab)
}


tab_c05800_reform <- function(diffs, pdigits=c(0, 0, rep(1, 7))) {
  tab <- diffs %>%
    select(reform_name, ftype, agirange, value=c05800.reform) %>%
    spread(ftype, value) %>%
    mutate(cart.diff=cart - puf,
           rf.diff=rf - puf,
           cart.pdiff=cart.diff / puf * 100,
           rf.pdiff=rf.diff / puf * 100) %>%
    kable(caption="Tax before credits, reform, $ billions",
          digits=pdigits,
          format.args=list(big.mark=",")) %>%
    kable_styling(full_width = FALSE)
  return(tab)
}


tab_c05800_diffs <- function(diffs, pdigits=c(0, 0, rep(1, 7))) {
  tab <- diffs %>%
    select(reform_name, ftype, agirange, value=diff) %>%
    spread(ftype, value) %>%
    mutate(cart.diff=cart - puf,
           rf.diff=rf - puf,
           cart.pdiff=cart.diff / puf * 100,
           rf.pdiff=rf.diff / puf * 100) %>%
    kable(caption="Change in tax before credits, $ billions",
          digits=pdigits,
          format.args=list(big.mark=",")) %>%
    kable_styling(full_width = FALSE)
  return(tab)
}

tab_c05800_pdiffs <- function(diffs, pdigits=c(0, 0, rep(1, 7))){
  tab <- diffs %>%
    select(reform_name, ftype, agirange, value=pdiff) %>%
    spread(ftype, value) %>%
    mutate(cart.diff=cart - puf,
           rf.diff=rf - puf) %>%
    kable(caption="% change in tax before credits",
          digits=pdigits) %>%
    kable_styling(full_width = FALSE)
  return(tab)
}


```


```{r low_match_functions}

tab_c05800_lm <- function(diffs, pdigits=c(0, 0, rep(1, 7))) {
  tab <- diffs %>%
    select(reform_name, ftype, agirange, value=c05800) %>%
    spread(ftype, value) %>%
    mutate(syn.diff=syn - puf,
           syn.pdiff=syn.diff / puf * 100) %>%
    kable(caption="Tax before credits, baseline, $ billions",
          digits=pdigits,
          format.args=list(big.mark=",")) %>%
    kable_styling(full_width = FALSE)
  return(tab)
}


tab_c05800_reform_lm <- function(diffs, pdigits=c(0, 0, rep(1, 7))) {
  tab <- diffs %>%
    select(reform_name, ftype, agirange, value=c05800.reform) %>%
    spread(ftype, value) %>%
    mutate(cart.diff=cart - puf,
           rf.diff=rf - puf,
           cart.pdiff=cart.diff / puf * 100,
           rf.pdiff=rf.diff / puf * 100) %>%
    kable(caption="Tax before credits, reform, $ billions",
          digits=pdigits,
          format.args=list(big.mark=",")) %>%
    kable_styling(full_width = FALSE)
  return(tab)
}


tab_c05800_diffs_lm <- function(diffs, pdigits=c(0, 0, rep(1, 7))) {
  tab <- diffs %>%
    select(reform_name, ftype, agirange, value=diff) %>%
    spread(ftype, value) %>%
    mutate(cart.diff=cart - puf,
           rf.diff=rf - puf,
           cart.pdiff=cart.diff / puf * 100,
           rf.pdiff=rf.diff / puf * 100) %>%
    kable(caption="Change in tax before credits, $ billions",
          digits=pdigits,
          format.args=list(big.mark=",")) %>%
    kable_styling(full_width = FALSE)
  return(tab)
}

tab_c05800_pdiffs_lm <- function(diffs, pdigits=c(0, 0, rep(1, 7))){
  tab <- diffs %>%
    select(reform_name, ftype, agirange, value=pdiff) %>%
    spread(ftype, value) %>%
    mutate(cart.diff=cart - puf,
           rf.diff=rf - puf) %>%
    kable(caption="% change in tax before credits",
          digits=pdigits) %>%
    kable_styling(full_width = FALSE)
  return(tab)
}
```



# Rate cut analysis
```{r , include=FALSE}
# put this before each run
reform <- "rate_cut"
# reform <- "reform4"
mrgdf <- get_mrgdf(reform)
diffs <- get_diffs(mrgdf)
```


## Tax before credits, baseline
Table shows baseline amount in $ billions, cart and rf minus puf, and cart and rf % difference from puf
```{r rows.print=20}
# tab_taxbc(diffs)
tab_c05800(diffs)

```


## Tax before credits, reform
Table shows reform amount in $ billions, cart and rf minus puf, and cart and rf % difference from puf
```{r rows.print=20}
# tab_taxbc_reform(diffs)
tab_c05800_reform(diffs)

```


## Change in tax before credits, reform vs. baseline
Table shows change from puf to cart and rf in $ billions, cart and rf change minus puf change, and % difference of cart and rf $ changes from puf $ change
```{r rows.print=20}
tab_c05800_diffs(diffs)
```

## Percentage change in tax before credits, reform vs. baseline
Table shows percentage change from baseline to reform, plus cart and rf % change minus puf % change
```{r rows.print=20}
tab_c05800_pdiffs(diffs)
```




# Rate cut analysis -- lowmatch file
```{r , include=FALSE}
# put this before each run
reform <- "rate_cut"
# reform <- "reform4"
mrgdf <- get_mrgdf(reform, "lowmatch")
diffs <- get_diffs(mrgdf)
```


## Tax before credits, baseline -- lowmatch file
Table shows baseline amount in $ billions, cart and rf minus puf, and cart and rf % difference from puf
```{r rows.print=20}
# tab_taxbc(diffs)
tab_c05800_lm(diffs)

```


## Tax before credits, reform -- lowmatch file
Table shows reform amount in $ billions, cart and rf minus puf, and cart and rf % difference from puf
```{r rows.print=20}
# tab_taxbc_reform(diffs)
tab_c05800_reform(diffs)

```


## Change in tax before credits, reform vs. baseline -- lowmatch file
Table shows change from puf to cart and rf in $ billions, cart and rf change minus puf change, and % difference of cart and rf $ changes from puf $ change
```{r rows.print=20}
tab_c05800_diffs(diffs)
```

## Percentage change in tax before credits, reform vs. baseline -- lowmatch file
Table shows percentage change from baseline to reform, plus cart and rf % change minus puf % change
```{r rows.print=20}
tab_c05800_pdiffs(diffs)
```



# Trump 2013 tax cut analysis
```{r , include=FALSE}
# put this before each run
reform <- "Trump2013"
mrgdf <- get_mrgdf(reform)
diffs <- get_diffs(mrgdf)
```


## Tax before credits, baseline
Table shows baseline amount in $ billions, cart and rf minus puf, and cart and rf % difference from puf
```{r rows.print=20}
tab_c05800(diffs)

```


## Tax before credits, reform
Table shows reform amount in $ billions, cart and rf minus puf, and cart and rf % difference from puf
```{r rows.print=20}
tab_c05800_reform(diffs)

```


## Change in tax before credits, reform vs. baseline
Table shows change from puf to cart and rf in $ billions, cart and rf change minus puf change, and % difference of cart and rf $ changes from puf $ change
```{r rows.print=20}
tab_c05800_diffs(diffs)
```

## Percentage change in tax before credits, reform vs. baseline
Table shows percentage change from baseline to reform, plus cart and rf % change minus puf % change
```{r rows.print=20}
tab_c05800_pdiffs(diffs)
```


# brk4_2013 $100 reduction in lower income threshold at which 33% rate applies (Dan's brk5, I think)
```{r , include=FALSE}
# put this before each run
reform <- "brk4_2013"
mrgdf <- get_mrgdf(reform)
diffs <- get_diffs(mrgdf)
```


## Tax before credits, baseline
Table shows baseline amount in $ billions, cart and rf minus puf, and cart and rf % difference from puf
```{r rows.print=20}
tab_c05800(diffs)

```


## Tax before credits, reform
Table shows reform amount in $ billions, cart and rf minus puf, and cart and rf % difference from puf
```{r rows.print=20}
tab_c05800_reform(diffs)

```


## Change in tax before credits, reform vs. baseline
Table shows change from puf to cart and rf in $ billions, cart and rf change minus puf change, and % difference of cart and rf $ changes from puf $ change
```{r rows.print=20}
tab_c05800_diffs(diffs)
```

## Percentage change in tax before credits, reform vs. baseline
Table shows percentage change from baseline to reform, plus cart and rf % change minus puf % change
```{r rows.print=20}
tab_c05800_pdiffs(diffs)
```

# brk4_2013 $10k reduction in lower income threshold at which 33% rate applies (Dan's brk5, I think)
```{r , include=FALSE}
# put this before each run
reform <- "brk4_10k_2013"
mrgdf <- get_mrgdf(reform)
diffs <- get_diffs(mrgdf)
```


## Tax before credits, baseline
Table shows baseline amount in $ billions, cart and rf minus puf, and cart and rf % difference from puf
```{r rows.print=20}
tab_c05800(diffs)

```


## Tax before credits, reform
Table shows reform amount in $ billions, cart and rf minus puf, and cart and rf % difference from puf
```{r rows.print=20}
tab_c05800_reform(diffs)

```


## Change in tax before credits, reform vs. baseline
Table shows change from puf to cart and rf in $ billions, cart and rf change minus puf change, and % difference of cart and rf $ changes from puf $ change
```{r rows.print=20}
tab_c05800_diffs(diffs)
```


## Percentage change in tax before credits, reform vs. baseline
Table shows percentage change from baseline to reform, plus cart and rf % change minus puf % change
```{r rows.print=20}
tab_c05800_pdiffs(diffs)
```


# amtex $1k reduction in amt exemption
```{r include=FALSE}
# put this before each run
reform <- "amtex_2013"
mrgdf <- get_mrgdf(reform)
diffs <- get_diffs(mrgdf)

```


```{r rows.print=20}
tab_c05800(diffs)
tab_c05800_reform(diffs)
tab_c05800_diffs(diffs)
tab_c05800_pdiffs(diffs)

```

# amtex $10k reduction in amt exemption
```{r include=FALSE}
# put this before each run
reform <- "amtex10k_2013"
mrgdf <- get_mrgdf(reform)
diffs <- get_diffs(mrgdf)

```


```{r rows.print=20}
tab_c05800(diffs)
tab_c05800_reform(diffs)
tab_c05800_diffs(diffs)
tab_c05800_pdiffs(diffs)

```

# Lower the 28% rate upper-bracket threshold
```{r include=FALSE}
# put this before each run
reform <- "brk4_1k_2013"
mrgdf <- get_mrgdf(reform)
diffs <- get_diffs(mrgdf)

```


```{r rows.print=20}
tab_c05800(diffs)
tab_c05800_reform(diffs)
tab_c05800_diffs(diffs, pdigits=c(0, 0, rep(3, 3), rep(3, 2), rep(1, 2)))
tab_c05800_pdiffs(diffs)

```


# Tuition deduction elimination
```{r include=FALSE}
# put this before each run
reform <- "tuition0320_2013"
mrgdf <- get_mrgdf(reform)
diffs <- get_diffs(mrgdf)

```


```{r rows.print=20}
tab_c05800(diffs)
tab_c05800_reform(diffs)
tab_c05800_diffs(diffs, pdigits=c(0, 0, rep(3, 3), rep(3, 2), rep(1, 2)))
tab_c05800_pdiffs(diffs)

```


# Increase the 28% rate to 29%
```{r include=FALSE}
# put this before each run
reform <- "rt4_rate28_2013"
mrgdf <- get_mrgdf(reform)
diffs <- get_diffs(mrgdf)

```


```{r rows.print=20}
tab_c05800(diffs)
tab_c05800_reform(diffs)
tab_c05800_diffs(diffs, pdigits=c(0, 0, rep(3, 3), rep(3, 2), rep(1, 2)))
tab_c05800_pdiffs(diffs)

```

# Winners and losers reform4
```{r , include=FALSE}
# put this before each run
reform <- "reform4"
mrgdf <- get_mrgdf(reform)
diffs <- get_diffs(mrgdf)
```


## Tax before credits, baseline
Table shows baseline amount in $ billions, cart and rf minus puf, and cart and rf % difference from puf
```{r rows.print=20}
tab_c05800(diffs)

```


## Tax before credits, reform
Table shows reform amount in $ billions, cart and rf minus puf, and cart and rf % difference from puf
```{r rows.print=20}
tab_c05800_reform(diffs)

```


## Change in tax before credits, reform vs. baseline
Table shows change from puf to cart and rf in $ billions, cart and rf change minus puf change, and % difference of cart and rf $ changes from puf $ change
```{r rows.print=20}
tab_c05800_diffs(diffs)
```

## Percentage change in tax before credits, reform vs. baseline
Table shows percentage change from baseline to reform, plus cart and rf % change minus puf % change
```{r rows.print=20}
tab_c05800_pdiffs(diffs)
```



## Detailed breakdown of winners and losers for complex reform (reform4)
```{r include=FALSE}
# reform <- "reform4"
# mrgdf <- get_mrgdf(reform)
# diffs <- get_diffs(mrgdf)
# names(mrgdf) %>% sort

# create a df that has 3 marital statuses plus ALL, and has winners divided from losers, and ALL
detail <- mrgdf %>%
  mutate(winlose=case_when(c05800.reform < c05800 ~ "win",
                             c05800.reform > c05800 ~ "lose",
                             c05800.reform==c05800 ~ "draw",
                             TRUE ~ "ERROR"),
         agirange=cut(c00100, iranges, include.lowest=TRUE, labels=irange_labs),
         # add placeholders for totals to our grouping variables as we will add totals below
         agirange=fct_expand(agirange, "Total"),
         msname=fct_expand(msname, "Total"),
         winlose=fct_expand(winlose, "Total")) %>%
  group_by(reform_name, ftype, msname, winlose, agirange) %>%
  summarise(nretk=sum(wt) / 1e3,
            c05800=sum(c05800 * wt) / 1e9,
            c05800.reform=sum(c05800.reform * wt) / 1e9)

# add all income ranges to detail
detail_inc <- detail %>%
  group_by(reform_name, ftype, msname, winlose) %>% # agirange left out
  summarise_at(vars(nretk, c05800, c05800.reform), ~sum(.)) %>%
  mutate(agirange="Total", agirange=factor(agirange, levels=levels(detail$agirange))) %>%
  bind_rows(detail) # combine with prior df

# add all marital statuses to detail_inc
detail_incmars <- detail_inc %>%
  group_by(reform_name, ftype, agirange, winlose) %>% # msname left out
  summarise_at(vars(nretk, c05800, c05800.reform), ~sum(.)) %>%
  mutate(msname="Total", msname=factor(msname, levels=levels(detail$msname))) %>%
  bind_rows(detail_inc) # combine with prior df

# add all win-lose status to detail_incmars
detail_incmarswl <- detail_incmars %>%
  group_by(reform_name, ftype, agirange, msname) %>% # winlose left out
  summarise_at(vars(nretk, c05800, c05800.reform), ~sum(.)) %>%
  mutate(winlose="Total", winlose=factor(winlose, levels=levels(detail$winlose))) %>%
  bind_rows(detail_incmars) # combine with prior df

# make sure we have the right number of counts - drop agirange for size
count(detail_incmarswl %>% ungroup, ftype, msname, winlose)

# add calculated variables
detail_full <- detail_incmarswl %>%
  mutate(diff=c05800.reform - c05800,  pdiff=diff / c05800 * 100) %>%
  ungroup %>%
  arrange(reform_name, ftype, msname, winlose)

g <- function(msname.in, winlose.in, var) {
  tab <- detail_full %>%
    filter(msname==msname.in, winlose==winlose.in) %>%
    select(reform_name, ftype, msname, winlose, agirange, value=var) %>%
    mutate(vname=var) %>%
    spread(ftype, value) %>%
    mutate(diff.cart=cart - puf, diff.rf=rf - puf)
  if(var != "pdiff") tab <- tab %>% mutate(pdiff.cart=diff.cart / puf * 100, pdiff.rf=diff.rf / puf * 100)
  tab %>%
    kable(digits=c(rep(0, 5), rep(1, 7)), format.args = list(big.mark=",")) %>%
    kable_styling(full_width = FALSE)
}
# g("Total", "Total", "nretk")

gsum <- function() {
  tab <- detail_full %>%
    filter(msname=="Total", agirange=="Total", winlose!="draw") %>%
    select(ftype, winlose, c05800, c05800.reform, diff, pdiff)
} 

```


### Number of winners and losers (thousands)
#### Total number of winners and losers (not by marital status) (thousands)
```{r}
g("Total", "Total", "nretk")
g("Total", "win", "nretk")
g("Total", "lose", "nretk")
g("Total", "draw", "nretk")

```

#### Married number of winners and losers (thousands)
```{r}
g("married", "Total", "nretk")
g("married", "win", "nretk")
g("married", "lose", "nretk")
g("married", "draw", "nretk")

```

#### Single number of winners and losers (thousands)
```{r}
g("single", "Total", "nretk")
g("single", "win", "nretk")
g("single", "lose", "nretk")
g("single", "draw", "nretk")

```

#### Other marital status number of winners and losers (thousands)
```{r}
g("other", "Total", "nretk")
g("other", "win", "nretk")
g("other", "lose", "nretk")
g("other", "draw", "nretk")

```

### Tax change ($ billions): winners and losers
#### Tax change total ($ billions): winners and losers (not by marital status)
```{r}
g("Total", "Total", "diff")
g("Total", "win", "diff")
g("Total", "lose", "diff")
g("Total", "draw", "diff")

```

#### Tax change married ($ billions): winners and losers
```{r}
g("married", "Total", "diff")
g("married", "win", "diff")
g("married", "lose", "diff")
g("married", "draw", "diff")

```

#### Tax change single ($ billions): winners and losers
```{r}
g("single", "Total", "diff")
g("single", "win", "diff")
g("single", "lose", "diff")
g("single", "draw", "diff")

```





